A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2021-03-19 manuscript.Rmd
update Dockerfile example in manuscript

# Define the R version to be installed from rocker project
FROM rocker/verse:3.6.1
# install CRAN R packages: pacman, here, and pander
RUN install2.r --error --skipinstalled\
  pacman here pander
# install additional R packages from github: papaja and wordcountaddin
RUN installGithub.r\
  crsh/papaja benmarwick/wordcountaddin
# set the working directory inside the container
WORKDIR /home/rstudio
```

>>>>

# Define the R version to be installed from rocker project
FROM rocker/verse:3.6.1
# install CRAN R packages: pacman, here, and pander
RUN install2.r --error --skipinstalled\
  pacman here pander
# install additional R packages from github: papaja and wordcountaddin
# the package version if fixed by hash (user/package@hash)
RUN installGithub.r\
  crsh/papaja@b6cd70f benmarwick/wordcountaddin@fdf70d9
# set the working directory inside the container
WORKDIR /home/rstudio
```
